---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# ```rrcov```: Scalable Robust Estimators with High Breakdown Point

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/rrcov)](https://cran.r-project.org/package=rrcov)
[![R-CMD-check](https://github.com/valentint/rrcov/workflows/R-CMD-check/badge.svg)](https://github.com/valentint/rrcov/actions)
[![downloads](https://cranlogs.r-pkg.org/badges/rrcov)](https://cran.r-project.org/package=rrcov)
<!-- badges: end -->

The package ```rrcov``` provides scalable robust estimators with high breakdown point and covers a large number of robustified multivariate analysis methods, starting with robust estimators for the multivariate location and covariance matrix (MCD, MVE, S, MM, SD), the deterministic versions of MCD, S and MM estimates and regularized versions (MRCD) for high dimensions. These estimators are used to conduct robust principal components analysis (```PcaCov()```), linear and quadratic discriminant analysis (```Linda()```, ```Qda()```), MANOVA. Projection pursuit algorithms for PCA to be applied in high dimensions are also available (```PcaHubert()```, ```PcaGrid()``` and ```PcaProj()```).

## Installation

The `rrcov` package is on CRAN (The Comprehensive R Archive Network) and
the latest release can be easily installed using the command

    install.packages("rrcov")
    library(rrcov)

## Building from source

To install the latest stable development version from GitHub, you can
pull this repository and install it using

    ## install.packages("remotes")
    remotes::install_github("valentint/rrcov" --no-build-vignettes)

Of course, if you have already installed `remotes`, you can skip the
first line (I have commented it out).

## Example

This is a basic example which shows you if the package is properly installed:

```{r example}

library(rrcov)
data(hbk)
(out <- CovMcd(hbk))

```

